### 2021-07-15 src/paper/report.tex
shorten.

In the model, susceptibility to contracting the SARS-CoV-2 virus is dependent on age. A
possible infection progresses as shown in Figure~\ref{fig:model_disease_progression}. We
differentiate between an initial period of infection without being infectious or showing
symptoms, being infectious (presymptomatic or asymptomatic), showing symptoms, requiring
intensive care, and recovery or death \citep[similar to][]{Aleta2020}. The calibration
of the age dependent probabilities of transitioning between these states  is described
in Supplementary Material~\ref{sub:data_course_of_disease}). Conditional on the type of
contact, infectiousness is independent of age \citep{Jones2021}.

>>>>

In the model, a possible infection progresses as shown in
Figure~\ref{fig:model_disease_progression} (similar to \cite{Aleta2020}, more in
Supplementary Material~\ref{sub:data_course_of_disease}). Whereas susceptibility to the
viruses differs by age, the infection probabilities are independent of age conditioned
on the type of contact \cite{Jones2021}.
